Matching bullets

### 2015-11-16 imaging-paper.Rnw
Residual plots

>>>>

A single cylinder as a fit is unlikely to be a particularly good fit; because there seem to be quite massive deformations in vertical direction. We therefore fit a circle for each cross section of the bullet, and compare the figure again:

<<bullet1, echo=FALSE, cache=TRUE>>=
db1 <- NULL
for (i in 1:6) {
  bname <- sprintf(file.path(datadir, "Br1 Bullet 1-%d.x3p"), i)
  dbi <- fortify_x3p(read.x3p(bname))
  dbi$part <- i
  db1 <- rbind(db1, dbi)
}

db1 <- db1 %>% group_by(part, x) %>% do (
    data.frame(., predCircle(.$y, .$value))
  )
@

<<bullet2, echo=FALSE, cache=TRUE>>=
db2 <- NULL
for (i in 1:6) {
  bname <- sprintf(file.path(datadir, "Br1 Bullet 2-%d.x3p"), i)
  dbi <- fortify_x3p(read.x3p(bname))
  dbi$part <- i
  db2 <- rbind(db2, dbi)
}

db2 <- db2 %>% group_by(part, x) %>% do (
    data.frame(., predCircle(.$y, .$value))
  )

@

First attempt to match - something is wrong with  piece 3 of bullet 2.

<<echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE>>=
qplot(y, resid, data=subset(db2, x <= 80 & x >=75), colour=factor(x)) + 
  facet_wrap(~part) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_point(aes(y, resid), colour="black", size=1, alpha=0.2, 
             data = filter(db1, part==1, x <= 80, x >=75)[,c("y", "resid")]) + ggtitle("Part 1 of Bullet 1 in black")
@
